Conditional selectivity for triplestores

### 2012-09-19 conditional/trunk/selectivity-basic.tex
add BGP section
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@386 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

\subsection{Extension to Basic Graph Patterns}

The statistics of Basic Graph Patterns, especially when involving
filters, are even more complex, and is likely to involve the use of
Bayesian Networks, which is beyond the scope of this paper. However,
as noted by \cite{splendid}, the intuition is that for some conjuctive
queries, the order of triples are not influenced by the conditionality
of separate triples. We believe the intuition is correct, but that in
detail, there are flaws in the argument of \cite{splendid}\todo{show
  counterexample}\todo{improve our own argument}.
